---
title: 'Ex. No : 3 - Augmenting the Thermal Conductivity of PCM Using CuO Nanoparticle'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 19BPS1014

### Name:  A.L.Viswanath

* * *
## Aim:

#To study and analyse the given liquid thermal conductivity dataset and plotting respective graphs using ANOVA technique in R.

## Setup
```{r}
rm(list=ls())
```

#Load necessary packages using library(packagename)
```{r}
library(dplyr)
library(readxl)
```

#Load the data
```{r}
d = read_excel("F:/sem - 6/CSE3506 - EDA/lab/lab 3/Maxwell_Liquid_Exp.xlsx",col_names = TRUE)
```


* * *

## Dataset Description

#Name of the Dataset
```{r}
liq_PCM = d
```


#Description of the fields
```{r}
names(liq_PCM)
```


#Basic commands to describe dataset
```{r}
str(liq_PCM)
```

```{r}
head(liq_PCM)
```

```{r}
summary(liq_PCM)
```

* * *

## Questions followed by corresponding Code & Output

#1. Determine the grand mean, and mean of thermal conductivity.
```{r}
print(paste('Mean of % inc in thermal(Analytical way - Maxwell Garnett)  :' ,mean(liq_PCM$`%Inc in K(Anal)`)))
print(paste('Mean of % inc in thermal(Expermintal way)  :' ,mean(liq_PCM$`%Inc in K(Exp)`)))

grandmean = (mean(liq_PCM$`%Inc in K(Anal)`) + mean(liq_PCM$`%Inc in K(Exp)`))/2
print(paste('Grand Mean :' ,grandmean))
```

#2. Determine the Sum of Squares between and Sum of Squares within.
```{r}
liq_PCM = liq_PCM %>%
  mutate(`(K(anal)-M)^2` = (`%Inc in K(Anal)`-mean(liq_PCM$`%Inc in K(Anal)`))^2) %>%
  mutate(`(K(exp)-M)^2` = (`%Inc in K(Exp)`-mean(liq_PCM$`%Inc in K(Exp)`))^2)

SSC = nrow(liq_PCM)*(mean(liq_PCM$`%Inc in K(Anal)`)-grandmean)^2 + nrow(liq_PCM)*(mean(liq_PCM$`%Inc in K(Exp)`)-grandmean)^2
print(paste('Sum of square between  :' ,SSC))

SSE = sum(liq_PCM$`(K(anal)-M)^2`) + sum(liq_PCM$`(K(exp)-M)^2`)
print(paste('Sum of square within  :' ,SSE))
```

#3. Degrees of Freedom (Between, Within and total)
```{r}
df_between = 2-1 # number of groups - 1 
print(paste('Degrees of Freedom between  :' ,df_between))

df_within = nrow(liq_PCM)*2 - 2 #number of rows of data - number of groups
print(paste('Degrees of Freedom within  :' ,df_within))

df_tot = nrow(liq_PCM)*2 - 1  #number of rows of data - 1
print(paste('Degrees of Freedom total  :' ,df_tot))
```

#4. Mean Squares (Between and Within)
```{r}
MSC = SSC/df_between
print(paste('Mean square between  :' ,MSC))

MSE = SSE/df_within
print(paste('Mean square within  :' ,MSE))
```

#5. F_Statistic and F Critical
```{r}
F_stat = MSC/MSE
print(paste('F_Statistic  :' ,F_stat))

F_crit = qf(0.05,df_between,df_within)
print(paste('F_Critical  :' ,F_crit))
```

#6. Check, Is Null hypothesize accepted?
```{r}
if(F_stat < F_crit){
  print(paste("NULL hypothesis is accepted."))
} else{
  print(paste("NULL hypothesis is not accepted."))
}
```

#7. Plot Vol. Concentration VS Thermal Conductivity
```{r}
plot(liq_PCM$`Vol. Conc.`,liq_PCM$`%Inc in K(Anal)`,type='b')
plot(liq_PCM$`Vol. Conc.`,liq_PCM$`%Inc in K(Exp)`,type='b')
```

#8. Plot Vol Concentration Vs % increase in Thermal conductivity –(In bar chart)
```{r}
barplot(liq_PCM$`Vol. Conc.`,liq_PCM$`%Inc in K(Anal)`,xlab="Vol. conc.",ylab="% inc in K(Anal)")
barplot(liq_PCM$`Vol. Conc.`,liq_PCM$`%Inc in K(Exp)`,xlab="Vol. conc.",ylab="% inc in K(Exp)")
```

#9. Error (Measured Value-Analytical Value)
```{r}
liq_PCM %>%
  mutate(Error = `%Inc in K(Exp)` - `%Inc in K(Anal)`)
```

* * *

