---
title: 'Ex. No :5 Logistic regression'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 19BPS1014

### Name:  A.L.Viswanath

* * *
## Aim:

#To study and analyse the given daibeties dataset using Logisic regression technique in R.

## Setup

#Load necessary packages using library(packagename)
```{r}
library(dplyr)
```


#Load the data
```{r}
data <- read.csv("F:/sem - 6/CSE3506 - EDA/lab/lab 5/diabetes.csv")
```


* * *

## Dataset Description

#Name of the Dataset
```{r}
diabetes <- data
```


#Description of the fields
```{r}
names(diabetes)
```


#Basic commands to describe dataset
```{r}
str(diabetes)
```

```{r}
sum(is.na(diabetes))
```

```{r}
summary(diabetes)
```

```{r}
diabetes
```

```{r}
diabetes$Outcome <- as.factor(diabetes$Outcome)
str(diabetes)
```

* * *

## Questions followed by corresponding Code & Output

#Model Fitting
```{r}
set.seed(54)
data <- sample(2,nrow(diabetes),replace = T, prob = c(0.75,0.25))
train = diabetes[data==1,]
test = diabetes[data==2,]
```

```{r}
lrmodel = glm(Outcome~Pregnancies+Glucose+BloodPressure+SkinThickness+Insulin+BMI+DiabetesPedigreeFunction+Age,train,family = "binomial")
summary(lrmodel)
```

```{r}
lrmodel = glm(Outcome~Pregnancies+Glucose+BMI,train,family = "binomial")
summary(lrmodel)
```

#Prediction
```{r}
pred <- predict(lrmodel,test,type = "response")
pred
```

```{r}
#confusion matrix
table(test$Outcome, pred > 0.5)
```

```{r}
pred_outcome <- ifelse(pred > 0.5, 1, 0)
acc = mean(pred_outcome == test$Outcome)
print(paste('Accuracy',acc))
```

* * *


