---
title: 'Ex. No :6 Naive bayes'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 19BPS1014

### Name:  A.L.Viswanath

* * *
## Aim:

#To study and analyse the given daibeties dataset using Naive Bayes technique in R.

## Setup

#Load necessary packages using library(packagename)
```{r}
#install.packages('naivebayes')
library(naivebayes)
library(dplyr)
```


#Load the data
```{r}
data <- read.csv("F:/sem - 6/CSE3506 - EDA/lab/lab 6/diabetes.csv")
```


* * *

## Dataset Description

#Name of the Dataset
```{r}
diabetes <- data
```


#Description of the fields
```{r}
names(diabetes)
```


#Basic commands to describe dataset
```{r}
str(diabetes)
```

```{r}
sum(is.na(diabetes))
```

```{r}
summary(diabetes)
```

```{r}
diabetes
```

```{r}
diabetes$Outcome <- as.factor(diabetes$Outcome)
str(diabetes)
```

* * *

## Questions followed by corresponding Code & Output

#Model Fitting
```{r}
set.seed(54)
data <- sample(2,nrow(diabetes),replace = T, prob = c(0.75,0.25))
train = diabetes[data==1,]
test = diabetes[data==2,]
```

```{r}
nbmodel <- naive_bayes(Outcome~.,train, usekernel = T) 
nbmodel
```
```{r}
plot(nbmodel) 
```

```{r}
summary(nbmodel)
```

#Prediction
```{r}
p <- predict(nbmodel, test, type = 'prob')
head(cbind(p, test))
```

```{r}
#confusion matrix
p <- predict(nbmodel, test)
tab <- table(p, test$Outcome)
per = 1 - sum(diag(tab)) / sum(tab)
print(paste('Missclassification(%): ',per))
```
* * *


