---
title: 'Ex. No : 2 - Solar Pond'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 19BPS1014

### Name:  A.L.Viswanath

* * *
## Aim: 

#To study and analyse the given solar pond dataset and plotting respective graphs.

## Setup
```{r}
rm(list=ls())
```


#Load necessary packages using library(packagename)
```{r}
library(ggplot2)
library(readxl)
```


#Load the data
```{r}
d = read_excel("F:/sem - 6/CSE3506 - EDA/lab/lab 2/solarpond.xlsx", sheet = "data",col_names = TRUE)
d1 = read_excel("F:/sem - 6/CSE3506 - EDA/lab/lab 2/solarpond.xlsx", sheet = "data1",col_names = TRUE)
d2 = read_excel("F:/sem - 6/CSE3506 - EDA/lab/lab 2/solarpond.xlsx", sheet = "data2",col_names = TRUE)
```

* * *

## Dataset Description

#Name of the Dataset
```{r}
data <- d
data1 <- d1
data2 <- d2
```

#Description of the fields
```{r}
names(data)
```

#Basic commands to describe dataset
```{r}
str(data)
```

```{r}
head(data)
```
```{r}
summary(data)
```

```{r}
summary(data1)
```

```{r}
summary(data2)
```
* * *

## Questions followed by corresponding Code & Output

#1. rbind (data1, dat2)
```{r}
datas <- rbind(data1,data2)
datas
```

#2. Store Temperature column : LCZ(TT=0), LCZ(TT=3), LCZ(TT=5), in variables V1, V2 and V3 respectively. Cbind all these three columns.
```{r}
V1 = datas$`LCZ(0)`
V2 = datas$`LCZ(3)`
V3 = datas$`LCZ(5)`
cbind(V1,V2,V3)
```

#3. Plot Time Vs Pyranometer reading of ‘data’ for the month May
```{r}
plot(datas$Time,datas$`Pyranometer reading`)
```


#4. Plot Pyranometer reading Vs Two
```{r}
par(mfrow=c(2,3))
plot(datas$`Pyranometer reading`,datas$`Two(0)`,pch=3)
plot(datas$`Pyranometer reading`,datas$`Two(3)`,pch=17)
plot(datas$`Pyranometer reading`,datas$`Two(5)`,pch=4)
```

```{r}
plot(datas$`Pyranometer reading`,datas$`Two(0)`,pch=3,col='green')
points(datas$`Pyranometer reading`,datas$`Two(3)`,pch=2,col='red')
points(datas$`Pyranometer reading`,datas$`Two(5)`,pch=1,col='blue')
```

#5. Plot Pyranometer reading Vs Qact
```{r}
par(mfrow=c(2,3))
plot(datas$`Pyranometer reading`,datas$`Qact(0)`,pch=3)
plot(datas$`Pyranometer reading`,datas$`Qact(3)`,pch=17)
plot(datas$`Pyranometer reading`,datas$`Qact(5)`,pch=4)
```

```{r}
plot(datas$`Pyranometer reading`,datas$`Qact(0)`,pch=3,col='green')
points(datas$`Pyranometer reading`,datas$`Qact(3)`,pch=2,col='red')
points(datas$`Pyranometer reading`,datas$`Qact(5)`,pch=1,col='blue')
```

#6. Pyranometer reading Vs degree of temperature rise (T1)
```{r}
par(mfrow=c(2,3))
plot(datas$`Pyranometer reading`,datas$`DT1(0)`,pch=3)
plot(datas$`Pyranometer reading`,datas$`DT1(3)`,pch=17)
plot(datas$`Pyranometer reading`,datas$`DT1(5)`,pch=4)
```

```{r}
plot(datas$`Pyranometer reading`,datas$`DT1(0)`,pch=3,col='green')
points(datas$`Pyranometer reading`,datas$`DT1(3)`,pch=2,col='red')
points(datas$`Pyranometer reading`,datas$`DT1(5)`,pch=1,col='blue')
```

#7. Determine the best linear fit equation between Pyranometer reading and Two/Qact/Efficiency/Effectiveness
```{r}
model = lm(`Pyranometer reading`~`efficiency(3)`,data=data2)
model$coefficients
summary(model)
sigma(model)
```
#8. Plot the best linear fit
```{r}
ggplot(data2,aes(x=`Pyranometer reading`,y=`efficiency(3)`))+geom_point()+geom_smooth(method='lm',se=FALSE)
```

#9. Determine the Residual Sum of Squares (RSS)
```{r}
print(paste('Residual sum of squares :' ,deviance(model)))
```

#10. Plot the residuals.
```{r}
plot(resid(model),data2$`efficiency(3)`)
abline(0,0)
hist(model$residuals)
qqnorm(model$residuals,ylab="Residuals")
qqline(model$residuals)
```

* * *


