---
title: 'Ex. No : 1 - Regression'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 19BPS1014

### Name:  A.L.Viswanath

* * *
## Aim: Regression analysis on the given data set

## Setup
```{r}
rm(list=ls())
```

#Load necessary packages using library(packagename)
```{r}
library(dplyr)
library(ggplot2)
```

#Load the data
```{r}
data <- read.csv("F:/sem - 6/CSE3506 - EDA/lab/CreditWorthiness.csv")
```


* * *

## Dataset Description

#Name of the Dataset
```{r}
creditworth <- data
```

#Description of the fields
```{r}
names(creditworth)
```

#Basic commands to describe dataset
```{r}
str(creditworth)
```

```{r}
head(creditworth)
```

```{r}
summary(creditworth)
```


* * *

## Performing the set of instrution on given dataset.

## PLOTTING

###Since the linear relation is identeifies of any numberical and floating points, hence the integer data is analysed for the relation.
```{r}
ggplot(creditworth,aes(x=Cdur,y=InRate))+geom_point() #To plot - Cdur/InRate
ggplot(creditworth,aes(x=Cdur,y=InRate))+geom_point()+geom_smooth(method='lm',se=FALSE)
cor.test(creditworth$Cdur,creditworth$InRate)   # to find the correlation value
```
```{r}
ggplot(creditworth,aes(x=age,y=Cdur))+geom_point() #To plot - Cdur/InRate
ggplot(creditworth,aes(x=age,y=Cdur))+geom_point()+geom_smooth(method='lm',se=FALSE)
cor.test(creditworth$Cdur,creditworth$age)   # to find the correlation value
```
```{r}
ggplot(creditworth,aes(x=Camt,y=Cdur))+geom_point() #To plot - Cdur/InRate
ggplot(creditworth,aes(x=Camt,y=Cdur))+geom_point()+geom_smooth(method='lm',se=FALSE)
cor.test(creditworth$Cdur,creditworth$Camt)   # to find the correlation value
```

## SIMPLE LINEAR REGRESSION
```{r}
slr = lm(Camt~Cdur, creditworth) 
summary(slr)
plot(slr$resid)  # Residual plot
qqnorm(slr$resid,ylab="Residuals")   #Q-Q Plot
qqline(slr$resid)
```
```{r}
slr = lm(age~Cdur, creditworth) 
summary(slr)
plot(slr$resid)  # Residual plot
qqnorm(slr$resid,ylab="Residuals")   #Q-Q Plot
qqline(slr$resid)
```
## MULTIPLE LINEAR REGRESSION
```{r}
mlr = lm(Cdur~age+Camt, creditworth) 
summary(mlr)
plot(mlr$resid)  # Residual plot
qqnorm(mlr$resid,ylab="Residuals")   #Q-Q Plot
qqline(mlr$resid)
```

* * *
## Conclusion
Hence, SLR and MLR are inplemented and analysed.

* * *

