---
title: 'Ex. No 4 : Time Series Forecasting'
output:
  pdf_document: default
  word_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 19BPS1014

### Name:  A.L.Viswanath

* * *
## Aim:

#To study / implement .....

## Setup
```{r}
rm(list=ls())
```


#Load necessary packages using library(packagename)
```{r}
library(dplyr)
# install.packages("forecast")
# install.packages("tseries")
library("tseries")
library("forecast")
library(ggplot2)
```

#Load the data
```{r}
data(AirPassengers)
data <- AirPassengers
```

* * *

## Dataset Description

#Name of the Dataset
```{r}
passenger <- data
```

#Description of the fields
```{r}
passenger
```

#Basic commands to describe dataset
```{r}
summary(passenger)
```
```{r}
str(passenger)
frequency(passenger)
```


* * *

## Questions followed by corresponding Code & Output

#(i)Display entire dataset
```{r}
passenger
```

#(ii)Check for unfilled data
```{r}
sum(is.na(passenger))
```

#(ii) Display the statistical info of the dataset such as min, max, 1st quartile, 3rd quartile, mean and median.
```{r}
summary(passenger)
```

#(iii) Plot ‘data’ (No. of Air passengers Vs Year)
```{r}
plot(passenger,xlab="Year", ylab = "Passengers (1000's)",main="Air Passengers from 1949 to 1961")
```

#(iv) Plot as timeseries ‘data’ (monthwise)
```{r}
boxplot(passenger~cycle(passenger),xlab="Month(number)", ylab = "Passengs (1000's)" ,main ="Monthly Air Passengers Boxplot from 1949 to 1961")
```

#(v) Decompose the data as multiplicative and store as ‘ddata’
```{r}
ddata <- decompose(passenger,"multiplicative")
ddata
```

#(vi) Plot ‘ddata’
```{r}
autoplot(ddata)
```

#(vii) Plot the following: trend, seasonal and random separately.
```{r}
autoplot(ddata$trend)
autoplot(ddata$seasonal)
autoplot(ddata$random)
```

#(viii) Perform ADF test for stationarity
```{r}
adf.test(passenger)
```

#(ix) Plot ACF and PACF
```{r}
#ACF 
autoplot(acf(passenger,plot=FALSE))+ labs(title="ACF plot of Air Passengers from 1949 to 1961")
#PACF
autoplot(pacf(passenger,plot=FALSE))+ labs(title="PACF plot of Air Passengers from 1949 to 1961")
```

#(x) Model using ARIMA
```{r}
arimapassenger <- auto.arima(passenger)
arimapassenger
```

* * *

